### 2012-05-12 inst/examples/value_under_allee.Rmd
value under allee -- value_of_information, but with allee model

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=5 or`

@@

``` {r }
f <- BevHolt
````

Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)

``` {r }
BevHolt
````

That is, \\( f(x,h) = \frac{A x}{1 + B x} \\)

Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.  Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e. uses `sapply`), an annoying feature of `R` for users comming from Matlab.

We must now define parameters for the function.  Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), which we'll store for future reference as `K`.

``` {r }
pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
````

and we use a harvest-based profit function with default parameters

@@

The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).  Note that the R code defines a function from another function using a trick known as a _closure_.  Again we could write a custom profit function as long as it can take a vector stock size `x` and a scalar harvest level `h`.  Details for provided functions can be found in the manual, i.e. `?profit_harvest`.

>>>>

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=7 or`

@@

``` {r }
f <- Myer_harvest
pars <- c(1, 2, 6) 
p <- pars # shorthand 
K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2
x0 <- K - sigma_g ^ 2 / 2 
````

Take a look at the model:

``` {r }
f
````

We use a harvest-based profit function with default parameters

@@

The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).
